%
% File ucca_parsing.tex
%

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{url}
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{latexsym}
\usepackage{pgfplotstable}
\usepackage{algorithm2e}
\usepackage{hhline}
\usepackage{multirow}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\usepackage{tikz}
\usepackage{tikz-dependency}
\usetikzlibrary{shapes,fit,calc,er,positioning,intersections,decorations.shapes,mindmap,trees}
\tikzset{decorate sep/.style 2 args={decorate,decoration={shape backgrounds,shape=circle,
      shape size=#1,shape sep=#2}}}

\newcommand{\oa}[1]{\footnote{\color{red} #1}}
\newcommand{\daniel}[1]{\footnote{\color{blue} #1}}
\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}
\SetKwRepeat{Do}{do}{while}
\renewcommand\AlCapFnt{\normalfont\small}

\makeatletter
\renewcommand{\paragraph}{
  \@startsection{paragraph}{4}
  {\z@}{.5ex \@plus .5ex \@minus .2ex}{-1em}
  {\normalfont\normalsize\bfseries}
}
\makeatother

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

% To expand the titlebox for more authors, uncomment
% below and set accordingly.
% \addtolength\titlebox{.5in}    

\newcommand\BibTeX{B\textsc{ib}\TeX}


\title{Broad-Coverage Semantic Parsing: A Transition-Based Approach}
  %General Transition-Based Broad-Coverage Semantic Parsing

\author{Daniel Hershcovich \and Omri Abend \and Ari Rappoport \\
  Institute of Computer Science \\
  Hebrew University of Jerusalem \\
  {\tt \{danielh,oabend,arir\}@cs.huji.ac.il}
}

\date{}


\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%     Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

  The representation of many common semantic phenomena requires 
  structural properties beyond those commonly used for syntactic parsing.
  We discuss a set of structural properties required for
  broad-coverage semantic representation, and note that existing
  parsers support some of these properties, but not all.
  %(representations supporting these properties are called {\it Broad-coverage Semantic Structures}, or BSS).
  The main contribution of this paper is in proposing
  two transition-based techniques for parsing such semantic structures:
  (1) applying conversion procedures to map them into related formalisms,
  and using existing state-of-the-art parsers on the converted representations;
  and (2) constructing a parser that directly supports the full set of properties.
  We obtain encouraging results, using the UCCA semantic representation, which
  supports our formal characterization, as a testbed.
  
  %We experiment with two types of semantic representations, obtaining
  %encouraging results.
  %Universal Conceptual Cognitive Annotation (UCCA) is a semantic grammatical scheme
  % that assigns 
  %a complete structure to natural language text. We present the first automatic
  % UCCA parser, 
  % a transition-based parser using a novel transition system. We compare the
  % results to baselines 
  % obtained by converting UCCA to CoNNL-X, and training syntactic parsers on the
  % converted dependency trees.
  
\end{abstract}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

In order to support the full range of semantic structures exhibited by
natural language, the following three structural properties should be supported.
The first is support for DAG, rather than tree structures,
in order to represent arguments and relations (semantic units)
that are shared between predicates.
For instance, in the sentence
``After graduation, John moved to Paris'', ``John'' is an argument of both ``graduation''
and ``moved'', yielding a DAG structure (\figref{fig:graduation}).
The second is support for non-terminal nodes, in order to represent units
comprising of more than one word.
While bi-lexical dependencies partially circumvent this restriction, by
representing complex units in terms of their headwords, they fall short
when representing units that have no clear head.
Frequent examples of such constructions include
coordination structures (e.g., ``{\bf John and Mary} went home''; \figref{fig:home}),
some multi-word expressions (e.g., ``The Haves and the {\bf Have Nots}''),
and prepositional phrases.
Third, semantic units may be discontiguous in the text. For instance, in ``John gave everything up''
(\figref{fig:gave}), the phrasal verb ``gave ... up'' forms a single semantic unit.
We call formal representations supporting all three properties
{\it Broad-coverage Semantic Structures} (BSS).

However, to our knowledge, no existing parser supports the combination of these criteria,
and the only semantically-annotated corpora that supports them is UCCA \cite{abend2013universal},
which has no parser.
Several other models either support some of these properties \cite{oepen2015semeval},
or avoid grounding semantic units altogether
(notably, AMR \cite{banarescu2013abstract}). See \secref{sec:background}.

In this work we are thus first in proposing techniques for BSS parsing.
We adopt a transition-based approach, which has recently produced some of the best
results in syntactic dependency parsing
\cite{dyer2015transition,ballesteros2015improved}, and has also demonstrated
strong performance in a variety of other semantic and syntactic settings,
e.g., \newcite{maier2015discontinuous,wang2015transition}.

We pursue two complementary parsing strategies.
First, we assess the ability of existing technology to tackle the task,
by developing conversion protocols between UCCA structures and two related formalisms:
dependency trees and discontiguous constituency trees.
As these formalisms are more restrictive than BSS, the conversion
is necessarily lossy. Nonetheless, we find that it is effective
in practice (\secref{sec:conversion_approach}).
Second, we present a novel transition-based broad-coverage parser,
Broad-coverage Semantic Parser (\textsc{bsp}; \secref{sec:direct_approach})
that supports BSS parsing, based on extending existing transition-based parsers
with new transitions and features. %for parsing BSS and UCCA in particular.
Transition-based methods are a natural starting point for UCCA parsing,
as the set of distinctions it represents, which is centered around predicate-argument
structures and their inter-relations, is similar in spirit to the distinctions
conveyed by dependency schemes.

We experiment with the English UCCA-annotated corpora \cite{abend2013universal}
as a test case,
and apply the parsing approaches both to in-domain and out-of-domain scenarios.
Results are encouraging, with nearly 70\% labeled F-score for the highest
scoring parser, and suggest concrete paths for further improvement.
All converters and parsers will be made publicly available upon publication.


%\footnote{While the task is not specific to UCCA,
%  to the best of our knowledge, UCCA's are the only
%  semantically annotated corpora that support all criteria of BSS.},
%a small degradation with the transition to out-of-domain scenarios.

%A general parser for this setting must support the prediction of multiple parents,
%as well as of discontiguous constituents, both pervasive phenomena in semantic
%structures even in English (see \secref{sec:data}.
%Multiple parents show up frequently in the context of argument
%sharing, where a certain argument participates in several relations but is only mentioned once.
%Common examples are coordination structures
%(e.g., in ``John went home and took a shower'', ``John'' is an argument of both ``went'' and ``took'')
%or nominalizations (e.g., ``After graduation, John moved to London'', where ``John'' is an argument
%of both ``graduation'' and ``moved'').
%Discontiguous units are common even in syntactic structures in some languages (e.g., German, Bulgarian,
%Korean and many others \cite{kallmeyer2013data}), and can even be found in English, e.g., in reported
%speech: ``'The dog', John said, 'is back again''', and are even more pervasive in English semantic parses
%(see \secref{sec:data}).

%\oa{fix this}
%The contribution of this work is thus three-fold.
%First, we motivate and define the broad-coverage semantic parsing task.
%Second, we create converters and study the ability of existing parsing technology
%for formally related settings to address the task, focusing on transition-based methods.
%Third, we present \textsc{bsp}, novel both in being the first broad-coverage DAG parser,
%as well as the first UCCA parser. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}\label{sec:background}

\begin{figure}
  \begin{subfigure}[t]{.5\textwidth}
  \centering
  \scalebox{.9}{
  \begin{tikzpicture}[level distance=10mm, ->]
    \node (ROOT) [fill=black, circle] {}
      child {node (After) {After} edge from parent node[left] {\scriptsize $L$}}
      child {node (graduation) [fill=black, circle] {}
      {
        child {node {graduation} edge from parent node[left] {\scriptsize $P$}}
      } edge from parent node[left] {\scriptsize $H$} }
      child {node {,} edge from parent node[right] {\scriptsize $U$}}
      child {node (moved) [fill=black, circle] {}
      {
        child {node (John) {John} edge from parent node[left] {\scriptsize $A$}}
        child {node {moved} edge from parent node[left] {\scriptsize $P$}}
        child {node [fill=black, circle] {}
        {
          child {node {to} edge from parent node[left] {\scriptsize $R$}}
          child {node {Paris} edge from parent node[left] {\scriptsize $C$}}
        } edge from parent node[left] {\scriptsize $A$} }
      } edge from parent node[right] {\scriptsize $H$} }
      ;
    \draw[dashed,->] (graduation) to node [auto] {\scriptsize $A$} (John);
    %\node (LKG) at (-1.8,0) [fill=black!20, circle] {};
      %    \draw[bend right] (LKG) to node [auto, left] {\scriptsize $LR$} (After);
      %    \draw (LKG) to[out=-60, in=190] node [below] {\scriptsize $LA\quad$} (graduation);
%    \draw (LKG) to[out=30, in=90] node [above] {\scriptsize $LA$} (moved);
  \end{tikzpicture}
  }
  \caption{}
  \label{fig:graduation}
  \end{subfigure}
%  \scalebox{.9}{
%  \begin{tikzpicture}[level distance=12mm, ->,
%      every node/.append style={midway}]
%    \node (ROOT) [fill=black, circle] {}
%      child {node (John) {John} edge from parent node[left] {\scriptsize $A$}}
%      child {node {decided} edge from parent node[left] {\scriptsize $P$}}
%      child {node (totakeaquickshower) [fill=black, circle] {}
%      {
%        child {node {to} edge from parent node[left] {\scriptsize $F$}}
%        child {node (takeashower) [fill=black, circle] {}
%        {
%          child {node {take} edge from parent node[left] {\scriptsize $C$}}
%          child {node {a} edge from parent node[right] {\scriptsize $F$}}
%          child {node (quick) {quick} edge from parent[white]}
%          child {node {shower} edge from parent node[right] {\scriptsize $C$}}
%        } edge from parent node[right] {\scriptsize $P$} }
%      } edge from parent node[left] {\scriptsize $A$} }
%      ;
%    \draw[bend left,dashed,->] (takeashower) to node [auto] {\scriptsize $A$} (John);
%    \draw[bend left,->] (totakeaquickshower) to node [auto] {\scriptsize $D$} (quick);
%  \end{tikzpicture}
%  }
  \begin{subfigure}[t]{.5\textwidth}
  \centering
  \scalebox{.9}{
  \begin{tikzpicture}[level distance=12mm, ->,
      every node/.append style={midway}]
    \node (ROOT) [fill=black, circle] {}
      child {node [fill=black, circle] {}
      {
        child {node {John} edge from parent node[left] {\scriptsize $C$}}
        child {node {and} edge from parent node[left] {\scriptsize $N$}}
        child {node {Mary} edge from parent node[left] {\scriptsize $C$}}
      } edge from parent node[left] {\scriptsize $A$} }
      child {node {went} edge from parent node[left] {\scriptsize $P$}}
      child {node {home} edge from parent node[left] {\scriptsize $A$}}
      ;
  \end{tikzpicture}
  }
  \caption{}
  \label{fig:home}
  \end{subfigure}
  \begin{subfigure}[t]{.5\textwidth}
  \centering
  \scalebox{.9}{
  \begin{tikzpicture}[level distance=12mm, ->,
      every node/.append style={midway}]
    \node (ROOT) [fill=black, circle] {}
      child {node {John} edge from parent node[left] {\scriptsize $A$}}
      child {node [fill=black, circle] {}
      {
      	child {node {gave} edge from parent node[left] {\scriptsize $C$}}
      	child {node (everything) {everything} edge from parent[white]}
      	child {node {up} edge from parent node[left] {\scriptsize $C$}}
      } edge from parent node[right] {\scriptsize $P$} }
      ;
    \draw[bend right,->] (ROOT) to[out=-20, in=180] node [left] {\scriptsize $A$} (everything);
  \end{tikzpicture}
  }
  \caption{}
  \label{fig:gave}
  \end{subfigure}
  \caption{\label{fig:examples}
    Semantic representation of the three structural properties
    required for BSS, according to the UCCA scheme. \subref{fig:graduation} includes a remote edge (dashed),
    resulting in ``John'' having two parents. % and a linkage relation (gray node and its outgoing edges).
    \subref{fig:home} includes a coordination construction (``John and Mary'').
    \subref{fig:gave} includes a discontiguous unit (``gave ... up'').
    Legend: $P$ -- a Scene's main relation, $A$ -- participant,
    $L$ -- inter-scene linker, $H$ -- linked Scene, $C$ -- center,
    $R$ -- relator, $N$ -- connector, $U$ -- punctuation, $F$ -- function unit.
    Pre-terminal nodes are omitted for brevity.
}
\end{figure}

\com{
\begin{figure*}
\begin{adjustbox}{width=\textwidth}
  \begin{tikzpicture}[level distance=20mm, ->,
  level 1/.style={sibling distance=8em},
  level 2/.style={sibling distance=4em},
  level 3/.style={sibling distance=4em}]
    \node (ROOT) [fill=black, circle] {}
      child {node [fill=black, circle] {}
      {
        child {node {A} edge from parent node[left] {\scriptsize $E$}}
        child {node {similar} edge from parent node[left] {\scriptsize $E$}}
        child {node {technique} edge from parent node[right] {\scriptsize $C$}}
      } edge from parent node[left] {\scriptsize $A\quad$ \hspace{1mm} } }
      child {node {is} edge from parent node[left] {\scriptsize $F$}}
      child {node [fill=black, circle] {}
      {
        child {node {almost} edge from parent node[left] {\scriptsize $E$}}
        child {node {impossible} edge from parent node[right] {\scriptsize $C$}}
      } edge from parent node[left] {\scriptsize $D$} }
      child {node {\textbf{IMPLICIT}} edge from parent node[left] {\scriptsize $A$}}
      child {node {to} edge from parent node[left] {\scriptsize $F$}}
      child {node {apply} edge from parent node[left] {\scriptsize $P\quad$}}
      child {node [fill=black, circle] {}
      {
        child {node {to} edge from parent node[left] {\scriptsize $R$}}
        child {node {other} edge from parent node[left] {\scriptsize $E$}}
        child {node {crops} edge from parent node[left] {\scriptsize $C$}}
        child {node {,} edge from parent node[left] {\scriptsize $U$}}
        child {node [fill=black, circle] {}
        {
          child {node {such as} edge from parent node[left] {\scriptsize $R$}}
          child {node {cotton} edge from parent node[left] {\scriptsize $C$}}
          child {node {,} edge from parent node[left] {\scriptsize $U$}}
          child {node {soybeans} edge from parent node[left] {\scriptsize $C$}}
          child {node {and} edge from parent node[left] {\scriptsize $N$}}
          child {node {rice} edge from parent node[right] {\scriptsize $\; C$}}
        } edge from parent node[right] {\scriptsize $\; E$ \hspace{1mm} } }
      } edge from parent node[left] {\scriptsize $A\;$ \hspace{1mm} } }
      child {node {.} edge from parent node[right] {\scriptsize $\quad \quad U$}}
      ;
  \end{tikzpicture}
\end{adjustbox}
\caption{\label{fig:ucca_example2}
  UCCA graph for the sentence ``A similar technique is almost impossible to
  apply to other crops, such as cotton, soybeans and rice.''
  The sentence was used by Oepen et al. (2015) to compare between the difference schemes. The sentence includes a single Scene, whose main relation is ``apply'', a secondary relation ``almost impossible'', as well as two complex arguments: ``a similar technique'' and the coordinated argument ``such as cotton, soybeans, and rice.''
}
\end{figure*}
}

\paragraph{The UCCA Annotation Scheme.}
Universal Cognitive Conceptual Annotation (UCCA)
is a cross-linguistically applicable semantic representation scheme,
that builds on the established ``Basic Linguistic Theory'' framework for typological description
\cite{Dixon:10b,Dixon:10a,Dixon:12}, and on the Cognitive Linguistics literature.
UCCA is a multi-layered representation, where each layer corresponds to a ``module'' of
semantic distinctions (e.g., predicate-argument structures, adverbials, coreference etc.).
Importantly, the same set of categories can be applied across different lexical items and languages.
This stands in contrast to more schemes such as FrameNet \cite{Baker:98},
PropBank \cite{Palmer:05} and AMR, that define an open-ended, lexically-based set of categories,
which while providing further information, are more prone to coverage issues \cite{Palmer:10},
and may result in a different set of relations when applied to different languages \cite{Xue2014not}.

Formally, a UCCA structure over a sentence is a DAG, whose leaves correspond to the sentence's words.
The nodes of the graph, or its ``units'', are either terminals or several
sub-units (not necessarily contiguous) jointly viewed as a
single entity according to some semantic or cognitive consideration.
Edges bear a category, indicating the role of the sub-unit in the relation that the parent represents.
UCCA structures support all three criteria of BSS: multiple parents, non-terminal nodes, and discontiguous units.

UCCA's foundational layer, which we use here, covers the predicate-argument
structures evoked by predicates of all grammatical categories
(verbal, nominal, adjectival and others), the inter-relations between them,
as well as other major linguistic phenomena such as coordination and multi-word expressions.
This set of categories has demonstrated applicability to multiple languages, including
English, French, German and Czech, support for rapid annotation, and semantic stability in translation:
UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2015conceptual}. This finding supports the claim that UCCA represents an abstract
level of semantics, shared by different languages.

The layer's basic notion is the {\it Scene}, which describes a movement, an action or a state.
Each Scene contains one Main Relation, as well as one or more Participants.
For example, the sentence ``After graduation, John moved to Paris'' contains two Scenes,
whose main relations are ``graduation'' and ``moved''. ``John'' is a Participant in both Scenes,
while ``Paris'' only of the latter.
We note that the scheme marks one of the incoming edges for each non-root
as ``primary'' and the others as ``remote'' edges.
The two Scenes in this sentence are both arguments of the \textit{Linker} ``After'',
which in this case expresses a temporal relation between them.
\figref{fig:examples} presents the UCCA annotation of this and other examples.

Further categories account for relations between Scenes and the internal structures of
complex arguments (e.g., coordination) and relations
(e.g., complex adverbials, such a ``very clearly''). UCCA graphs may contain implicit
units that have no correspondent in the text, but the parsing of these
units is deferred to future work, as it is likely to require different methods
than those explored here \cite{roth2015inducing}.

%The example ``John decided to take a shower'' contains two Scenes, whose main relations are ``decided'' and ``take a shower'', and where the second Scene is a participant in the first.
%The participant ``John'' is a part of both Scenes, but is marked as a \textit{remote} participant in
%the second, since it is not explicit in the second clause.

\paragraph{Broad-coverage Semantic Representation.}
While earlier work on semantic parsing has mostly concentrated on shallow semantic analysis,
focusing on semantic role labeling of verbal argument structures,
the focus has recently shifted to parsing of more elaborate representations that account
for a wider range of phenomena. 
Most closely related to this work is the Broad-coverage Semantic Dependency Parsing (SDP) task,
recently addressed in two SemEval tasks \cite{oepen2014semeval,oepen2015semeval},
experimenting with the Prague tectogrammatical layer \cite{bohmova2003prague},
and dependencies derived from the Enju parser\footnote{See \url{http://kmcs.nii.ac.jp/enju/}.},
and Lingo ERG \cite{Flic:02}.
Like BSS parsing, SDP addresses a wide range of semantic phenomena,
and supports discontiguous units and multiple parents. However, SDP uses
bi-lexical dependencies, disallowing non-terminal nodes, and thus faces difficulties in supporting
structures that have no clear head, such as coordination \cite{Ivanova2012who}.

Another line of work addressed parsing into Abstract Meaning Representations (AMRs)
\cite{flanigan2014discriminative,vanderwende2015amr,pust2015parsing,artzi2015broad}. 
While sharing much of this work's motivation, AMR parsing techniques are not applicable
here for two reasons. 
First, AMR does not ground its units in the words and constituents of the text.
This is both reflected in the representation scheme,
where not all nodes correspond to words in the text and vice versa, and in
parsing, as it requires that the alignment between words and logical symbols be
automatically detected, thus altering the parsing task.
\newcite{wang2015transition} applied a transition-based approach to AMR parsing,
but their method involved first syntactically parsing the input, and then converting
the resulting tree into an AMR. They thus used a different set of transitions than
\textsc{bsp}, which parses strings directly into graphs.





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conversion-Based Parsing}\label{sec:conversion_approach}

We begin by assessing the ability of existing technology to address the task,
by taking a conversion-based approach. Training proceeds by 
converting BSS into a different representation,
and training an existing parser on the converted structures.
We test the trained parsers by applying them to the test set,
and converting the results back to BSS, where they are compared
with the gold standard.
The error resulting from this back and forth conversion is discussed in
\secref{sec:results}.

\paragraph{Notation.}
Let $L$ be the set of possible edge labels.
A BSS is a directed acyclic graph $G=(V,E, \ell)$
over a sequence of tokens $w_1, \ldots, w_n$,
where $\ell:E\to L$ is a function of \textit{edge labels}.
For each token $w_i$ ($i=1, \ldots, n$), there exists a leaf (or a terminal) $t_i \in V$.

\paragraph{Conversion to Constituency Trees.}
We convert BSS to constituency trees by removing a subset of the
edges\footnote{For trees, labeling nodes is equivalent to labeling edges. Thus,
  we do not distinguish between the two options. 
  Note also that as the original structures may contain discontiguities, so may the resulting trees.}.
Specifically, when converting UCCA structures, we simply remove all remote edges,
leaving only primary edges that form a tree structure
(see \figref{fig:graduation}).
The inverse conversion from trees to BSS is simply the identity function, as every constituency tree is a BSS.

\paragraph{Conversion to Dependency Trees.}\label{subsec:con2dep}
In the conversion to dependency trees, we first convert BSS
to constituency trees using the above procedure, and then convert the result to dependency trees. 
Assume $T_c=(V_c,E_c,\ell_c)$ is a constituency tree with labels $\ell_c:E_c~\rightarrow~L$,
where $L$ is the set of possible labels.
The conversion from $T_c$ to a dependency tree involves the removal of
all non-terminals from $T_c$ and the addition of edges between terminals.
The nodes of the converted dependency tree are simply the terminals of $T_c$.

We define a linear order over possible edge labels $L$.
For each node $u \in V$, denote with $h(u)$ its child with the highest edge label.
Denote with $h^*(u)$ the terminal reached by recursively applying $h(\cdot)$ over $u$.
For each terminal $t$, we define $n(t)$ as the highest
non-terminal such that $t=h^*(n(t))$, i.e.,
$n(t)$ is the only node such that $t=h^*(n(t))$ and $t \neq h^*(\mathrm{Parent}_c(n(t)))$.
The head of $t$ according to the dependency graph is
the terminal $h^*(\mathrm{Parent}_c(n(t)))$.
The complete algorithm is given in Algorithm~\ref{alg:con2dep}.

We note that this conversion procedure is simpler than the
head percolation procedure used for converting syntactic constituency
trees to dependency trees.
This is because $h(u)$ of a node $u$ (similar to $u$'s head-containing child),
depends only on the label of the edge $(h(u),u)$, and not on the sub-tree spanned by $u$,
because edge labels in UCCA directly express the role of the child in the parent unit, and
are thus sufficient for determining which of $u$'s children contains the head node.
%This is appropriate, since edges in a semantic constituency graph express the relation between units,
%whereas in syntactic constituency trees the identity of a node depends on the nodes below it.

\begin{algorithm}[t]
  \small
  \KwData{constituency tree ${T_c}=(V_c,E_c,\ell_c)$}
 \KwResult{dependency tree $T_d=(V_d,E_d,\ell_d)$}
 \ForEach{$u \in V_c$} {
  $h(u) \leftarrow \argmin_v \mathrm{Priority}(\ell_c(u,v))$\;
 }
 $V_d \leftarrow \mathrm{Terminals}({T_c})$,
 $E_d \leftarrow \emptyset$\;
 \ForEach{$t \in V_d$} {
  $u \leftarrow t$\;
  \While{$u=h(\mathrm{Parent}_c(u))$} {
  	$h^*(u) \leftarrow t$\;
  	$u \leftarrow \mathrm{Parent}_c(u)$\;
  }
  $n(t) \leftarrow h(u)$\;
 }
 \ForEach{$t \in V_d$} {
  $u \leftarrow \mathrm{Parent}_c(n(t))$\;
  $t^\prime \leftarrow h^*(u)$\;
  $E_d \leftarrow E_d \cup \{(t^\prime, t)\}$\;
  $\ell_d (t^\prime, t) \leftarrow \ell_c(u, n(t))\}$\;
 }
 \caption{\small Constituency to dependency conversion procedure.}
 \label{alg:con2dep}
\end{algorithm}

The inverse conversion introduces non-terminal nodes back into the tree.
As the distinction between low- and high-attaching nodes is lost in the constituency to
dependency conversion, we heuristically assume that attachments are always
high-attaching.
Assume $T_d=(V_d,E_d,\ell_d)$ is a dependency tree.
We begin by creating a root node $r$.
Then, iterating over $V_d$ in topological order,
we add its members as terminals to the constituency tree
and create a pre-terminal parent for each,
with an edge labeled as \textit{Terminal} between them.
The parents of the pre-terminals are determined by the terminal's parent in the dependency
tree: if a dependency node $t$ is a child of the root in $T_d$, then $t$'s pre-terminal will also be a child of the root node. Otherwise, $t$'s pre-terminal is the child of the pre-terminal associated with $t$'s head in $T_d$. We add an intermediate node in between if $t$ has any dependents in $T_d$,
to allow adding their pre-terminals as children.
Edge labels for the intermediate edges are determined by a rule-based function, denoted by $\mathrm{Label}(u)$.
In practice, it mostly selects the UCCA label Center.

\begin{algorithm}
  \small
 \KwData{dependency tree $T_d=(V_d,E_d,\ell_d)$}
 \KwResult{constituency tree $T_c=(V_c,E_c,\ell_c)$}
 $r \leftarrow \mathrm{Node()}$\;
 $V_c \leftarrow \{r\}$,
 $E_c \leftarrow \emptyset$\;
 \ForEach{$t \in \mathrm{TopologicalSort}(V_d)$} {
  $u \leftarrow \mathrm{Node()}$\;
  $V_c \leftarrow V_c \cup \{u, t\}$\;
  $E_c \leftarrow E_c \cup \{(u, t)\}$\;
  $\ell_c(u,t)\leftarrow\mathit{Terminal}$\;
  $t^\prime \leftarrow \mathrm{Parent}_d(t)$\;
  \eIf{$t^\prime = \textsc{Root}$} {
   $E_c \leftarrow E_c \cup \{(r, u)\}$\;
   $\ell_c(r, u) \leftarrow \mathrm{Label}(r,u)$\;
  } {
   \eIf{$\exists v \in V_d : (t,v) \in E_d$} {
    $u^\prime \leftarrow \mathrm{Node()}$\;
    $E_c \leftarrow E_c \cup \{(u^\prime, u)\}$\;
    $\ell_c(u^\prime, u) \leftarrow \mathrm{Label}(u^\prime, u)$\;
   } {
    $u' \leftarrow u$\;
   }
   $p \leftarrow \mathrm{Parent}_c(t^\prime)$\;
   $E_c \leftarrow E_c \cup \{(p, u^\prime)\}$\;
   $\ell_c(p, u^\prime) \leftarrow \ell_d(t^\prime, t)$\;
  }
 }
 \caption{\small Dependency to constituency conversion procedure.}
 \label{alg:dep2con}
\end{algorithm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Broad-Coverage DAG Parsing}\label{sec:direct_approach}

We now turn to presenting the BSP parser,
a transition-based parser that supports the three criteria of broad-coverage
semantic structures.

Transition-based parsing \cite{Nivre03anefficient} creates the parse tree
as it scans the text from left to right.
The parse tree is created incrementally by applying a \textit{transition} at each step to the parser state,
defined using three data structures: a buffer $B$ of tokens and nodes to be processed,
a stack $S$ of nodes currently being processed,
and a graph $G=(V,E,\ell)$ of constructed nodes and labeled edges.
Some of the states are marked as \textit{terminal}, meaning that $G$ is the final output.
A classifier is used at each step to select the next transition based on features
that encode the parser's current state.
During training, an oracle creates training instances for the classifier,
based on the gold-standard annotation.

Despite being based on local decisions, transition-based methods have yielded excellent
results in a variety of parsing tasks.
Within syntactic dependency parsing, transition-based methods
have been successfully applied to corpora in many languages and domains, yielding some
of the best reported results \cite{dyer2015transition,ballesteros2015improved}. 
The approach has also yielded results comparable with the state-of-the-art in
constituency parsing \cite{sagae2005classifier,zhang2009transition,zhu2013fast},
discontiguous constituency parsing \cite{maier2015discontinuous},
as well as dependency DAG structures
\cite{sagae2008shift,tokgoz2015transition}, CCG structures \cite{ambati2015incremental}
and AMR parsing \cite{wang2015transition}.

\textsc{BSP} mostly builds on recent advances in discontiguous constituency
and dependency DAG parsing techniques, and further introduces novel UCCA-oriented features for parsing BSS.

\paragraph{Transition Set.}
Given a sequence of tokens $w_1, \ldots, w_n$, we predict a BSS $G$ whose leaves
correspond to  $w_1, \ldots, w_n$.
Parsing starts with a single node in the stack (the root node), and the input tokens
$w_1, \ldots, w_n$ in the buffer. The set of transitions is given in \figref{fig:transitions}.
In addition to the standard \textsc{Shift} and \textsc{Reduce} operations, 
we follow previous work in transition-based constituency parsing \cite{sagae2005classifier}, and include the \textsc{Node} transition for creating new non-terminal nodes.
Concretely, \textsc{Node$_X$} creates a new node on the buffer as a parent of the first element on the stack, with an $X$-labeled edge.


\begin{figure*}
\begin{adjustbox}{width=\textwidth,margin=3pt,frame}
\begin{tabular}{llll|l|llllc|c}
\multicolumn{5}{c|}{\textbf{\small Initial State}} & \multicolumn{6}{c}{\textbf{\small Final State}} \\
\textbf{\footnotesize Stack} & \textbf{\footnotesize Buffer} & \textbf{\footnotesize Nodes} & \multicolumn{1}{l}{\textbf{\footnotesize Edges}} & \multicolumn{1}{c|}{\textbf{\footnotesize Terminal?}} & \textbf{\footnotesize Stack} & \textbf{\footnotesize Buffer} & \textbf{\footnotesize Nodes} & \textbf{\footnotesize Edges} & \multicolumn{1}{c}{\textbf{\footnotesize Terminal?}} \\
$[\mathrm{root}]$ & $w_{1:n}$ & \multirow{2}{40pt}{$\{\mathrm{root}\} \cup w_{1:n}$} & \multicolumn{1}{l}{$\emptyset$} & \multicolumn{1}{c|}{$-$} & $\emptyset$ & $\emptyset$ & $V$ & $E$ & \multicolumn{1}{c}{$+$} \\ 
\multicolumn{5}{c|}{} \\
\multicolumn{5}{c|}{} \\
\hline
%\end{tabular}
%\end{adjustbox}
%\begin{adjustbox}{width=\textwidth,frame}
%\begin{tabular}{llll|l|llllc|l}
\multicolumn{4}{c|}{\textbf{\small Before Transition}} & \textbf{\small Transition} & \multicolumn{5}{c|}{\textbf{\small After Transition}} & \textbf{\small Condition} \\
\textbf{\footnotesize Stack} & \textbf{\footnotesize Buffer} & \textbf{\footnotesize Nodes} & \textbf{\footnotesize Edges} & & \textbf{\footnotesize Stack} & \textbf{\footnotesize Buffer} & \textbf{\footnotesize Nodes} & \textbf{\footnotesize Edges} & \textbf{\footnotesize Terminal?} & \\
$S$ & $x \;|\; B$ & $V$ & $E$ & \textsc{Shift} & $S \;|\; x$ & $B$ & $V$ & $E$ & $-$ & \\
$S \;|\; x$ & $B$ & $V$ & $E$ & \textsc{Reduce} & $S$ & $B$ & $V$ & $E$ & $-$ & \\
$S \;|\; x$ & $B$ & $V$ & $E$ & \textsc{Node$_X$} & $S \;|\; x$ & $y \;|\; B$ & $V \cup \{ y \}$ & $E \cup \{ (y,x)_X \}$ & $-$ &
$x \neq \mathrm{root}$ \\
%$S \;|\; x$ & $B$ & $V$ & $E$ & \textsc{Implicit$_X$} & $S \;|\; x$ & $y^* \;|\; B$ & $V \cup \{ y^* \}$ & $E \cup \{ (x,y^*)_X \}$ & $-$ &
%$x \not\in w_{1:n}$ \\
$S \;|\; y,x$ & $B$ & $V$ & $E$ & \textsc{Left-Edge$_X$} & $S \;|\; y,x$ & $B$ & $V$ & $E \cup \{ (x,y)_X \}$ & $-$ &
\multirow{4}{50pt}{\vspace{-5mm}\[\left\{\begin{array}{l}
x \not\in w_{1:n},\\
y \neq \mathrm{root},\\
y \not\leadsto_G x
\end{array}\right.\]} \\
$S \;|\; x,y$ & $B$ & $V$ & $E$ & \textsc{Right-Edge$_X$} & $S \;|\; x,y$ & $B$ & $V$ & $E \cup \{ (x,y)_X \}$ & $-$ & \\
$S \;|\; y,x$ & $B$ & $V$ & $E$ & \textsc{Left-Remote$_X$} & $S \;|\; y,x$ & $B$ & $V$ & $E \cup \{ (x,y)_X^* \}$ & $-$ & \\
$S \;|\; x,y$ & $B$ & $V$ & $E$ & \textsc{Right-Remote$_X$} & $S \;|\; x,y$ & $B$ & $V$ & $E \cup \{ (x,y)_X^* \}$ & $-$ & \\
$S \;|\; x,y$ & $B$ & $V$ & $E$ & \textsc{Swap} & $S \;|\; y$ & $x \;|\; B$ & $V$ & $E$ & $-$ &
$\mathrm{i}(x) < \mathrm{i}(y)$ \\
$[\mathrm{root}]$ & $\emptyset$ & $V$ & $E$ & \textsc{Finish} & $\emptyset$ & $\emptyset$ & $V$ & $E$ & $+$ & \\
\end{tabular}
\end{adjustbox}
\caption{\label{fig:transitions}
  The transition set of \textsc{bsp}. %Following standard practice,
  We write the stack with its top to the right and the buffer with its head to the left.
  $(\cdot,\cdot)_X$ denotes an $X$-labeled edge, and $(\cdot,\cdot)_X^*$ a remote $X$-labeled edge.
  $\mathrm{i}(x)$ is a running index for the created nodes.
  \textsc{Edge} transitions have an additional condition: the prospective child may not
  already have a primary parent.
}
\end{figure*}

%\textsc{Implicit$_X$} acts similarly, but the created node is a child instead,
%and is marked as \textit{implicit}, representing a unit that does not appear explicitly in the text.

\textsc{Left-Edge$_X$} and \textsc{Right-Edge$_X$} create a new primary $X$-labeled edge between the first two elements on the stack, where the parent is the left or the right node, respectively. As a UCCA node may only
have one incoming primary edge, \textsc{Edge} transitions are disallowed where the child node already
has an incoming primary edge.
\textsc{Left-Remote$_X$} and \textsc{Right-Remote$_X$} do the same, but the created edge is
marked as \textit{remote}. We distinguish between these two pairs of transitions, for the parser
to be able to determine whether an edge is a primary or a remote one.
In order to support the prediction of multiple parents, node and edge transitions do not automatically
apply \textsc{Reduce}. This is in line with other work on
transition-based DAG dependency parsing \cite{sagae2008shift,tokgoz2015transition}.
Once all edges for a particular node have been created, it is removed from the stack
by applying \textsc{Reduce}.

\textsc{Swap} allows handling discontiguous nodes, by popping the second
node on the stack and adding it to the top of the buffer, as with the similarly
named transition in previous work \cite{nivre2009non,maier2015discontinuous}.
Finally, \textsc{Finish} pops the root node and marks the state as terminal.

\paragraph{Features.}
\label{subsec:features}

\figref{fig:features} presents the feature templates used by the parser.
For some of the features, we used the notion of \textit{head word},
defined by the $h^*(\cdot)$ function (\secref{subsec:con2dep}).
While head words are not explicitly represented in the UCCA scheme, these
features proved useful as means of encoding word-to-word relations.

In addition to the binary features defined by the feature templates,
we employ a real-valued feature, \textbf{ratio}, corresponding to the ratio between the number of terminals to number of nodes
in the graph $G$. This novel feature serves as a regularizer for the creation of new nodes, and should be beneficial for other transition-based constituency parsers too.
Features are generally adapted from the related parsers of \newcite{zhang2009transition,zhu2013fast,tokgoz2015transition} and
\newcite{maier2015discontinuous}, with a small additional set of features encoding relevant information
for the novel \textsc{Left-Remote$_X$} and \textsc{Right-Remote$_X$} transitions.

% and \textsc{Implicit$_X$}

%$s_i$ and $b_i$ stand for the $i$th stack and buffer items respectively, $w$ stands for the head word, $t$ for its POS tag, $e$ for the head incoming edge label. Note that $e$ replaces $c$ (consituent label) from Maier~\shortcite{maier2015discontinuous}, since in UCCA the labels are on the edges rather than the units; and a unit may have more than one incoming edge. $l$ and $r$ ($ll$ and $rr$) represent the leftmost and rightmost children (grand-children) of the element; $u$ handles the unary case.
%Concerning the separator features, $p$ is a unique separator feature between the head words of $s_0$ and $s_1$; $q$ is the count of any separator features between them.
%$x$ denotes the gap type of a subgraph. There are three possible values, either "none" (fully continuous), "pass" (there is a gap at the root, i.e., this gap must be filled later further up in the graph), or "gap" (the root of this graph fills a gap, i.e., its children have gaps, but the root does not). Finally, $y$ is the sum of all gap lengths.

% FEATURES
\begin{figure}
  \begin{adjustbox}{margin=3pt,frame}

\begin{tabular}{>{\small}l}
{Features from \cite{zhang2009transition}:} \\
\textbf{unigrams} \\
$s_0te, s_0we, s_1te, s_1we, s_2te, s_2we, s_3te, s_3we,$ \\
$b_0wt, b_1wt, b_2wt, b_3wt,$ \\
$s_0lwe, s_0rwe, s_0uwe, s_1lwe, s_1rwe, s_1uwe$ \\
\textbf{bigrams} \\
$s_0ws_1w, s_0ws_1e, s_0es_1w, s_0es_1e, s_0wb_0w, s_0wb_0t,$ \\
$s_0eb_0w, s_0eb_0t, s_1wb_0w, s_1wb_0t, s_1eb_0w, s_1eb_0t,$ \\
$b_0wb_1w, b_0wb_1t, b_0tb_1w, b_0tb_1t$ \\
\textbf{trigrams} \\
$s_0es_1es_2w, s_0es_1es_2e, s_0es_1eb_0w, s_0es_1eb_0t,$ \\
$s_0es_1wb_0w, s_0es_1wb_0t, s_0ws_1es_2e, s_0ws_1eb_0t$ \\
\textbf{separator} \\
$s_0wp, s_0wep, s_0wq, s_0wcq, s_0es_1ep, s_0es_1eq,$ \\
$s_1wp, s_1wep, s_1wq, s_1weq$ \\
\\
\textbf{extended} \cite{zhu2013fast} \\
$s_0llwe, s_0lrwe, s_0luwe, s_0rlwe, s_0rrwe,$ \\
$s_0ruwe, s_0ulwe, s_0urwe, s_0uuwe, s_1llwe,$ \\
$s_1lrwe, s_1luwe, s_1rlwe, s_1rrwe, s_1ruwe$ \\
\\
\textbf{disco} \cite{maier2015discontinuous} \\
$s_0xwe, s_1xwe, s_2xwe, s_3xwe,$ \\
$s_0xte, s_1xte, s_2xte, s_3xte,$ \\
$s_0xy, s_1xy, s_2xy, s_3xy$ \\
$s_0xs_1e, s_0xs_1w, s_0xs_1x, s_0ws_1x, s_0es_1x,$ \\
$s_0xs_2e, s_0xs_2w, s_0xs_2x, s_0ws_2x, s_0es_2x,$ \\
$s_0ys_1y, s_0ys_2y, s_0xb_0t, s_0xb_0w$ \\
\\
{\footnotesize Features from \cite{tokgoz2015transition}:} \\
\textbf{counts} \\
$s_0P, s_0C, s_0wP, s_0wC, b_0P, b_0C, b_0wP, b_0wC$ \\
\textbf{edges} \\
$s_0s_1, s_1s_0, s_0b_0, b_0s_0, s_0b_0e, b_0s_0e$ \\
\textbf{history} \\
$a_0we, a_1we$ \\
\\
\textbf{remote} (Novel, UCCA-specific features) \\
$s_0R, s_0wR, b_0R, b_0wR$
\end{tabular}
\end{adjustbox}

\caption{\label{fig:features}
  Feature templates for \textsc{bsp}. Notation:
  $s_i$, $b_i$ are the $i$th stack and buffer items, respectively.
  $w$ and $t$ are the word form and part-of-speech tag of the terminal returned by the $h^*(\cdot)$ function (\secref{subsec:con2dep}).
  $e$ is the edge label to the node returned by the $h(\cdot)$ function.
  $l$, $r$ ($ll$, $rr$) are the leftmost and rightmost (grand)children, respectively.
  $u$ ($uu$) is the unary (grand)child, when only one exists.
  $p$ is a unique separator punctuation and $q$ is the separator count between $s_0$ and $s_1$.
  $x$ is the gap type (``none'', ``pass'' or ``gap'') at the sub-graph under the current node, and $y$ is the sum of gap lengths \protect\cite{maier2009characterizing}.
  $P$ and $C$ are the number of parents and children, respectively, and $R$ is the number of remote children.
  $a_i$ is the transition taken $i$ steps back.
  All feature templates correspond to binary features.
}
\end{figure}

\paragraph{Training.}
Following \newcite{maier2015discontinuous}, we use a linear classifier, using
the averaged structured perceptron algorithm for training it
\cite{Coll:04} with the \textsc{MinUpdate} \cite{cai2011language} procedure
(i.e., a minimum number of updates to a feature has to occur in training for it
to be included in the model). Inference is performed greedily (i.e., without beam search).

For training the local classifier, we use a dynamic oracle \cite{goldberg2012dynamic},
i.e., an oracle that outputs a set of optimal transitions: when any of them
is applied to the current parser state, the gold
standard graph is reachable from the resulting state.
For example, the oracle would predict a \textsc{Node} transition if the stack 
has on its top a parent in the gold graph that hasn't been created,
but would predict a \textsc{Right-Edge} transition if the second stack
element is a parent of the
first element according to the gold graph and the edge between them hasn't been created.
The transition predicted by the classifier is deemed correct
and is applied to the parser state to reach the subsequent state
if the transition is included in the set of optimal transitions.
Otherwise, a random optimal transition is applied
and the classifier's weights are updated according to the structured perceptron
update rule.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Experiments}\label{sec:experiments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Setup}\label{sec:exp_setup}

\paragraph{Data.}\label{sec:data}
We conduct our main experiments on the UCCA Wikipedia corpus (henceforth, \textit{Wiki}),
and use the English part of the UCCA \textit{Twenty Thousand Leagues Under the Sea} English-French parallel corpus (henceforth, \textit{20K Leagues}) as
out-of-domain data.\footnote{Both are available at \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}
\tabref{table:data} presents some statistics for the two corpora, demonstrating that while
the \textit{Wiki} corpus is over ten times larger, the overall statistics are
similar.
We use passages of indices up to 655
of the \textit{Wiki} corpus as our training set, passages 656--700 as development set,
and passages 701--695 as in-domain test set.
While UCCA edges can cross sentence boundaries, we adhere to the common
practice in semantic parsing and train our parsers on individual sentences,
discarding inter-relations between them (0.18\% of the edges).
We also discard linkage nodes and edges, as they often express inter-sentence
relations and are thus mostly redundant when applied at the sentence level,
as well as implicit nodes (\secref{sec:background}).
In the out-of-domain experiments, we apply the same parser
(trained on the \textit{Wiki} corpus) to the entire \textit{20K Leagues}
corpus as test set, without re-tuning any parameters.


\begin{table}
  \scalebox{.8}{
\begin{tabular}{l|ccc|c}
& \multicolumn{3}{c|}{Wiki} & 20K \\
& \small Train & \small Dev & \small Test & Leagues \\
\hline
\# passages & 281 & 35 & 43 & 154 \\
\# sentences & 4021 & 537 & 608 & 522 \\
\hline
\# nodes & 277,587 & 40,700 & 45,047 & 29,965 \\
\% terminal & 42.41 & 42.8 & 42.66 & 41.23 \\
\% non-term. & 57.59 & 57.20 & 57.34 & 58.77 \\
\% implicit & 0.29 & 0.35 & 0.27 & 0.8 \\
\% linkage & 0.92 & 0.96 & 0.9 & 1.25 \\
\% discont. & 0.52 & 0.55 & 0.47 & 0.79 \\
\% \textgreater 1 parent & 2.29 & 1.89 & 2.21 & 1.98 \\
\hline
\# edges & 272,018 & 39,660 & 44,139 & 28,723 \\
\% primary & 95.37 & 95.70 & 95.90 & 94.48 \\
\% remote & 1.69 & 1.24 & 1.32 & 2.19 \\
\% linkage & 2.94 & 3.06 & 2.78 & 3.33 \\
\hline
\multicolumn{3}{l}{\footnotesize Average per non-linkage non-terminal node} \\
%\# parents & 0.98 & 0.97 & 0.98 & 0.95 \\
\# children & 1.67 & 1.67 & 1.67 & 1.61 
\end{tabular}
}
\caption{Statistics of the \textit{Wiki} and \textit{20K Leagues} UCCA corpora.
All counts exclude the root node.
}
\label{table:data}
\end{table}

\paragraph{Evaluation.}
Since there are no standard evaluation measures for BSS, we define
two simple measures for comparing such structures.
Assume $G_p=(V_p,E_p,\ell_p)$ and $G_g=(V_g,E_g,\ell_g)$
are the predicted and gold-standard DAGs over the same
sequence of terminals $W = \{w_1,\ldots,w_n\}$, respectively.
For an edge $e=(u,v)$ in either graph,
where $u$ is the parent and $v$ is the child, define its yield $y(e) \subseteq W$ as the
set of terminals in $W$ that are descendants of $v$.
We define the set of \textit{mutual edges} between $G_p$ and $G_g$:

\vspace{-.6cm}

{\small
\begin{multline*}
    M(G_p,G_g) = \\
    \left\{(e_1,e_2) \in E_p \times E_g \;|\;
    y(e_1) = y(e_2) \wedge \ell_p(e_1)=\ell_g(e_2)\right\}
\end{multline*}
}

\vspace{-.6cm}

Labeled precision and recall are defined by dividing $|M(G_p,G_g)|$ by $|E_p|$ and $|E_g|$, respectively.
We report two variants of this measure, one where we consider only non-remote edges,
and another where we consider remote edges. We note that the measure collapses to the standard
PARSEVAL constituency evaluation measure if $G_p$ are $G_g$ are trees.
Punctuation marks are excluded from the evaluation, but not from the datasets.

%For the conversions, we use \textsc{NeGra export} as the format for
%constituency representation and \textsc{CoNLL-X} as the format for dependency representation.

\paragraph{Conversions.}
We explore two conversion scenarios: one into (possibly discontiguous) constituency trees,
and one into CoNLL-style dependencies. In the first setting we experiment with \textsc{uparse},
the only transition-based constituency parser, to our knowledge, able to parse trees with
discontiguous constituents.
In the second setting we use the MaltParser with arc-standard and
arc-eager transition sets \cite{nivre2007maltparser}\footnote{Preliminary
experiments with non-projective variants of MaltParser yielded lower scores than
projective ones, and were thus discarded from the final evaluation.},
and the stack LSTM-based arc-standard parser \cite{dyer2015transition}.
In the MaltParser, we use both SVM and perceptron classifiers, and report
results obtained with the SVM classifier, which are about 1\% F-score higher.
Default settings are used in all cases.
We do not use existing dependency DAG parsers since we could not obtain their code.
We note that \textsc{uparse} uses beam search by default,
with a beam size of 4, where the other parsers use greedy search.

%The LSTM parser uses the arc-standard transition set, and the MaltParser
%running MaltParser with arc-standard yielded nearly the same
%scores as arc-eager. \textsc{uparse}, in contrast, uses a larger transition
%set that allows discontiguous constituency tree parsing.
%\textsc{bsp} extends this set further, allowing for DAG parsing
%and UCCA-specific features.

%Parsers parameter of variation is the classifier used by each of the parsers.
%The LSTM parser is based on neural networks, whereas the highest scores for
%MaltParser were obtained with an SVM classifier.
%Both \textsc{uparse} and \textsc{bsp} use a linear classifier.

%We omit linkage edges and nodes, as these are not evaluated
%by the evaluation metrics yet and are not an essential part of the
%semantic parsing scheme.
%We also omit implicit nodes, leaving them for future work.

Upper bounds for the conversion-based methods are computed by applying
the conversion and inverse conversion on the gold standard
graphs and comparing them to the original gold standard.

\paragraph{\textsc{bsp}.}
We train \textsc{bsp} for 16 iterations, using a \textsc{MinUpdate} value of 5 and a constant learning rate of 1.
We use an \textsc{Importance} value of 2, doubling the weight updates
for gold \textsc{Swap} transitions to address the sparseness
of discontiguous structures, as in \cite{maier2015discontinuous}.
We train \textsc{bsp} both where remote edges
are included, and when they are excluded from the training data, to allow
more direct comparison with conversion-based methods that can only
predict trees.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{sec:results}

\tabref{table:results} presents the results of our main experiments, as well as
upper bounds for the conversion-based methods.
\textsc{bsp} obtains comparable F-scores to MaltParser and \textsc{uparse}
in terms of primary edges, but unlike them, is able to predict some
of the remote edges as well. 
Removing remote edges from the training data of \textsc{bsp} does not
change results considerably on the primary edges,
reducing them by 0.9\% F-score in the in-domain setting, but reduces
them by the same amount when applied out-of-domain. 
Out-of-domain results are largely comparable with the in-domain
results, demonstrating robustness by \textsc{bsp}
to domain variation.

The LSTM parser obtains the best results on primary edges,
with a considerable margin. Importantly, it obtains 9.1\%
F-score higher than the arc-standard MaltParser, which
mostly differ from it in its classifier.
This suggests that applying a similar LSTM-based approach to
training \textsc{bsp} is likely to improve results,
and further underscores the feasibility of the transition-based
approach for BSS parsing. 

%too practically turns the structure into a constituency tree, and raises the scores above two of the conversion-based parsers. However, the stack LSTM-based parser of Dyer et al.~\shortcite{dyer2015transition} still reaches the highest score.

%\textsc{bsp} obtains scores that are nearly identical to \newcite{maier2015discontinuous}
%and Nivre et al.~\shortcite{nivre2007maltparser} on primary edges, but also correctly
%predicts remote edges when trained on them.
%Training without linkage edges and implicit nodes improve the scores on primary edges, as a more simple model is easier to learn.

The conversion to constituency format only removes remote edges,
and thus obtains a perfect primary edge score.
The conversion to dependency format loses considerably more information, since
all of non-terminal nodes are lost and have to be reconstructed by a
simple rule-based inverse conversion. Both conversions yield zero scores on remote edges,
since these are invariably removed when converting to trees.

\begin{table}[ht]
  \scalebox{.8}{
\begin{tabular}{l|ccc|ccc}
& \multicolumn{3}{c|}{Primary} & \multicolumn{3}{c}{Remote} \\
& \textbf{LP} & \textbf{LR} & \textbf{LF} & \textbf{LP} & \textbf{LR} & \textbf{LF} \\
\hline
\multicolumn{4}{l}{\rule{0pt}{2ex} \footnotesize Constituency Tree Conversion} \\
\textsc{uparse} & 64 & 67.3 & 65.4 & $-$ & 0 & 0 \\
Upper Bound & 100 & 100 & 100 & $-$ & 0 & 0 \\
\hline
\multicolumn{4}{l}{\rule{0pt}{4ex} \footnotesize Dependency Tree Conversion} \\
Malt$_{\textrm{arc-standard}}$ & 63.4 & 57.3 & 60.1 & $-$ & 0 & 0 \\
Malt$_{\textrm{arc-eager}}$ & 63.9 & 57.9 & 60.5 & $-$ & 0 & 0 \\
LSTM & {\bf 73.2} & {\bf 66.2} & {\bf 69.2} & $-$ & 0 & 0 \\
Upper Bound & 93.8 & 83.7 & 88.4 & $-$ & 0 & 0 \\
\hline
\multicolumn{4}{l}{\rule{0pt}{4ex} \footnotesize Direct Approach} \\
\textsc{bsp} & 62.4 & 56 & 59 & 15.3 & 11.8 & 13.3 \\
\textsc{bsp}$_{\mathrm{Tree}}$ & 63.8 & 56.5 & 59.9 & $-$ & 0 & 0 \\
\hhline{=======}
\multicolumn{4}{l}{\rule{0pt}{4ex} \footnotesize Out-of-domain} \\
\textsc{bsp} & 60.6 & 53.9 & 57.1 & 20.2 & 10.3 & 13.6 \\
\textsc{bsp}$_{\mathrm{Tree}}$ & 60.2 & 52.8 & 56.2 & $-$ & 0 & 0 \\
\end{tabular}
}
\caption{
  Main experimental results in percents. Columns correspond to labeled precision,
  recall and F-score for the different parsers, for both primary (left-hand side)
  and remote (right-hand side) edges. Top: results for \textsc{uparse}
  after conversion to constituency tree annotation. Upper middle: results for the
  MaltParser arc-eager and arc-standard, as well as
  the LSTM parser after conversion to dependency tree annotation.
  Lower middle: results for our \textsc{bsp}, when trained on the complete UCCA DAGs (\textsc{bsp}),
  and when trained on UCCA trees, obtained by removing remote edges (\textsc{bsp}$_{\mathrm{Tree}}$).
  Bottom: results for \textsc{bsp} and \textsc{bsp}$_{\mathrm{Tree}}$ when tested on out-of-domain data.
}
\label{table:results}
\end{table}

\paragraph{Feature Ablation.}
In order to evaluate the relative importance of the different feature sets,
we perform feature ablation experiments on \textsc{bsp},
removing a single set of features at a time,
and evaluating the resulting parser on the development set (\tabref{table:ablation}).
Results show that in the few cases where a feature set had only a small
or a negative contribution to the primary edge F-score, 
it had a positive contribution on the prediction of
remote edges.\oa{say something about what features are most important}


\begin{table}[ht]
  \scalebox{.8}{
\begin{tabular}{l|ccc|ccc}
& \multicolumn{3}{c|}{Primary} & \multicolumn{3}{c}{Remote} \\
& \textbf{LP} & \textbf{LR} & \textbf{LF} & \textbf{LP} & \textbf{LR} & \textbf{LF} \\
\hline
\textsc{bsp} &  &  &  &  &  &  \\
\textsc{bsp}$-$\textbf{unigrams} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{bigrams} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{trigrams} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{separator} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{extended} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{disco} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{counts} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{edges} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{history} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{remote} &  &  &  &  &  & \\
\textsc{bsp}$-$\textbf{ratio} &  &  &  &  &  &
\end{tabular}
}
\caption{
  Results in percents for the feature ablation experiment.
  Rows correspond to the BSP parser, where one feature set is excluded.
  Columns are the same as in \tabref{table:results}. 
  See \secref{subsec:features} and \figref{fig:features} for the definition of each feature set.
}
\label{table:ablation}
\end{table}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec:conclusion}

We have introduced the first parser that supports multiple parents, non-terminal
nodes and discontiguous units.
We further explored a conversion-based parsing approach in order to assess the ability of existing
technology to address the task.
The work makes a further contribution by first experimenting on UCCA parsing.
Results show that UCCA can already be parsed with 69.2\% F-score,
and suggests means for improvement by taking an LSTM-based
approach to the local classifier of \textsc{bsp}.
The quality of the results is underscored by UCCA's inter-annotator
agreement (often taken as an upper bound) of 
80--85\% F-score on primary edges \cite{abend2013universal}.

%In order to allow insight into the contribution of each of the feature sets,
%we conduct feature ablation experiments, and report results on the development set.
%Results show ...

%We will briefly review their results:
%(1) We applied the parsers to complete paragraphs, without splitting to sentences. MaltParser and the
%LSTM parser reached nearly the same scores as in the sentence experiments, but \textsc{uparse}
%and \textsc{bsp} failed to run with input above 500 tokens, for technical reasons.
%%%%%%%(2) We tried including linkage nodes and edges and implicit nodes when running \textsc{bsp}, by including them in the oracle output, allowing multiple non-remote parents and adding an additional \textsc{Implicit} transition. The scores were lower by 2 to 5 percentage points, as our classifier had to learn a more complex model, and our evaluation scheme does not yet support linkage and implicit.
%(3) We created a conversion procedure to SDP (semantic dependency parsing), an additional dependency format that allows multiple parents \cite{oepen2015semeval}. The resulting upper bound for primary edges was similar to the \textsc{CoNLL} format, but for remote edges it was as high as 68.6\% labeled F-score.


While much recent work focused on semantic parsing of different types,
the relations between the different representations have not been clarified.
We intend to further explore conversion-based parsing approaches to shed light
on the commonalities and differences between representations, suggesting ways to
design better semantic representations.
We believe that UCCA's merits in providing a cross-linguistically applicable, broad-coverage
annotation will support ongoing efforts to incorporate deeper semantic structures
into a variety of applications, such as machine translation \cite{jones2012semantics}
and summarization \cite{liu2015toward}.

%\paragraph{Improving the conversion procedure.}
%Several decision have to be made in the conversion between dependency and constituency annotation.
%%In the conversion from constituency to dependency, a head terminal has to be selected for each node. When converting in the other direction, labels for the added edges have to be determined.
%Currently, we handle these decisions by crude heuristics, but a more sophisticated way can be devised. These will be reflected by higher scores for the oracle experiments.

%\paragraph{Improving the direct parser.}
%%Our parser reaches promising results, but it is very basic in terms of the techniques used in it. Using beam search rather than greedy inference tends to improve the parsing scores significantly.
%In terms of machine learning, we use a linear classifier with hand-crafted features. As the experiment with the LSTM parser shows, implementing a parser based on neural networks should also give a significant improvement to our parsing scores.

\com{
Semantic parsing methods can be largely partitioned into grammar-based and grammarless methods.
Within the grammar-based literature, most work relied on Combinatory Categorial Grammar (CCG)
\cite{Steedman:00}, which allows to compute semantic structure compositionally from the
syntactic derivations. Notable examples include the Boxer parser \cite{bos2005towards}
and the AMR parser by \newcite{artzi2015broad}.
Other examples include parsing with Hyperedge Replacement Grammars
\cite{jones2012semantics,chiang2013parsing,peng2015synchronous} and
graph grammars \cite{koller2015semantic}.
A different line of work takes a discriminative, grammarless approach,
pursuing either graph-based methods that predict the highest ranking graph
(tree or DAG) that satisfies a given set of constraints
(e.g., \newcite{flanigan2014discriminative} for AMR parsing)
or a transition-based method that builds the parse incrementally following a series of local
decisions \cite[and much subsequent work]{Nivre03anefficient}.
}



\bibliography{references}
\bibliographystyle{acl2016}

\end{document}
